---
title: "TCGA_Example"
author: "Kai"
date: "5/1/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

This is an R Example to analyze TCGA data download using TCGABIOLINKS in R https://bioconductor.org/packages/release/bioc/html/TCGAbiolinks.html

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## Load Data
```{r}
setwd("/Users/kaiyuan/Desktop/TCGA/")
load("COAD_RNASeq_HTSeq.RData")
load("COAD_miRNASeq_HTSeq.RData")
```
organize the data in new data.frame format:
```{r}
miRNA_list<-data.frame(col_name=colnames(COAD_MiRNA_Matrix),
                       sampleID=sapply(colnames(COAD_MiRNA_Matrix), function(x) strsplit(x,"_")[[1]][3]),
                       site=sapply(colnames(COAD_MiRNA_Matrix), function(x) strsplit(x,"-")[[1]][4]))
miRNA_list<-miRNA_list[-1,]

mRNA_list<-data.frame(col_name=colnames(COAD_Matrix),
                      sampleID=colnames(COAD_Matrix),
                      site=sapply(colnames(COAD_Matrix), function(x) strsplit(x,"-")[[1]][4]))
```
select primary solid tumor using 01A 
```{r}
mRNA_list<-mRNA_list[mRNA_list$site %in% "01A",]
miRNA_list<-miRNA_list[miRNA_list$site %in% "01A",]

mRNA_list$patientID<-sapply(mRNA_list$sampleID,function(x) paste(strsplit(as.character(x),"-")[[1]][1],
                                                                 strsplit(as.character(x),"-")[[1]][2],
                                                                 strsplit(as.character(x),"-")[[1]][3],
                                                                 sep = "-"))
miRNA_list$patientID<-sapply(miRNA_list$sampleID,function(x) paste(strsplit(as.character(x),"-")[[1]][1],
                                                                 strsplit(as.character(x),"-")[[1]][2],
                                                                 strsplit(as.character(x),"-")[[1]][3],
                                                                 sep = "-"))
```
find matched samples
```{r}
mRNA_list<-mRNA_list[mRNA_list$patientID %in% intersect(mRNA_list$patientID,miRNA_list$patientID),]
miRNA_list<-miRNA_list[miRNA_list$patientID %in% intersect(mRNA_list$patientID,miRNA_list$patientID),]
```
extract data from expression table
```{r}
COAD_RNASeq_exp<-data.frame(COAD_Matrix[,colnames(COAD_Matrix) %in% mRNA_list$col_name])
COAD_miRNASeq_exp<-COAD_MiRNA_Matrix
rownames(COAD_miRNASeq_exp)<-COAD_MiRNA_Matrix$miRNA_ID
COAD_miRNASeq_exp<-COAD_miRNASeq_exp[,colnames(COAD_miRNASeq_exp) %in% miRNA_list$col_name]
```
pick gene of interest
```{r}
miR34a<-COAD_miRNASeq_exp[rownames(COAD_miRNASeq_exp) %in% "hsa-mir-34a",]
```
Gene Symbol	to Ensembl Gene ID  
IL17A=ENSG00000112115  
RORC=ENSG00000143365  
IL6R=ENSG00000160712  
IL23R=ENSG00000162594  
CCL22=ENSG00000102962  
IL17RD=ENSG00000144730  
IL17RA=ENSG00000177663  
```{r}
genelist<-COAD_RNASeq_exp[rownames(COAD_RNASeq_exp) %in% c("ENSG00000112115","ENSG00000143365",
                                                           "ENSG00000160712","ENSG00000162594",
                                                           "ENSG00000102962","ENSG00000144730","ENSG00000177663"),]
```
reorganize column name
```{r}
colnames(genelist)<-sapply(colnames(genelist), function(x) paste(strsplit(x,"[.]")[[1]][1],
                                                                 strsplit(x,"[.]")[[1]][2],
                                                                 strsplit(x,"[.]")[[1]][3],
                                                                 strsplit(x,"[.]")[[1]][4],sep = "-"))
colnames(miR34a)<-sapply(colnames(miR34a), function(x) paste(strsplit(strsplit(x,"_")[[1]][3],"-")[[1]][1],
                                                             strsplit(strsplit(x,"_")[[1]][3],"-")[[1]][2],
                                                             strsplit(strsplit(x,"_")[[1]][3],"-")[[1]][3],
                                                             strsplit(strsplit(x,"_")[[1]][3],"-")[[1]][4],sep = "-"))

miR34a_t<-data.frame(sampleID=colnames(miR34a),
                     miR34a=t(miR34a))
genelist_t<-data.frame(sampleID=colnames(genelist),
                       CCL22=t(genelist["ENSG00000102962",]),
                       IL17A=t(genelist["ENSG00000112115",]),
                       RORC=t(genelist["ENSG00000143365",]),
                       IL23R=t(genelist["ENSG00000162594",]),
                       IL6R=t(genelist["ENSG00000160712",]),
                       IL17RD=t(genelist["ENSG00000144730",]),
                       IL17RA=t(genelist["ENSG00000177663",]))


colnames(genelist_t)<-c("sampleID","CCL22","IL17A","RORC","IL23R","IL6R","IL17RD","IL17RA")


total_list<-merge(miR34a_t,genelist_t,by="sampleID")
total_list$ID<-paste(total_list$sampleID,rownames(total_list),sep = "-")
rownames(total_list)<-total_list$ID
total_list<-total_list[,-c(1,dim(total_list)[2])]
```
organize matrix for plotting
```{r}
library(corrplot)
#M<-cor(total_list[2:9])
#corrplot.mixed(M, upper="ellipse",mar = c(2, 2, 2, 2),title="total samples")
total_list$submitter_id<-sapply(rownames(total_list),function(x) strsplit(x,"-01")[[1]][1])
total_list<-merge(total_list,clinical,by="submitter_id")
total_list$tumor_stage[total_list$tumor_stage %in% c("stage i","stage ia")]<-"stage i"
total_list$tumor_stage[total_list$tumor_stage %in% c("stage iia","stage iib","stage ii","stage iic")]<-"stage ii"
total_list$tumor_stage[total_list$tumor_stage %in% c("stage iiia","stage iiib","stage iiic","stage iii")]<-"stage iii"
total_list$tumor_stage[total_list$tumor_stage %in% c("stage iva","stage ivb","stage iv")]<-"stage iv"
```
Correlation Plot
```{r}
library(lattice)
total_list_i<-total_list[total_list$tumor_stage %in% "stage i",]
M_i<-cor(total_list_i[2:9])
corrplot.mixed(M_i, upper="ellipse",mar = c(2, 2, 2, 2),title = "stage I")

total_list_ii<-total_list[total_list$tumor_stage %in% "stage ii",]
M_ii<-cor(total_list_ii[2:9])
corrplot.mixed(M_ii, upper="ellipse",mar = c(2, 2, 2, 2),title = "stage II")

total_list_iii<-total_list[total_list$tumor_stage %in% "stage iii",]
M_iii<-cor(total_list_iii[2:9])
corrplot.mixed(M_iii, upper="ellipse",mar = c(2, 2, 2, 2),title = "stage III")

total_list_iv<-total_list[total_list$tumor_stage %in% "stage iv",]
M_iv<-cor(total_list_iv[2:9])
corrplot.mixed(M_iv, upper="ellipse",mar = c(2, 2, 2, 2),title = "stage IV")
```